---
title: "Introduction"
author: "Sam McAllister"
format: html
editor: visual
---

## Dataset

We'll be using the **UK Demographic dataset** on Moodle <https://moodle.gla.ac.uk/mod/book/view.php?id=5162592>.

We'll use this dataset to explore morphological parameters and [covariables](https://research-coaches.com/dictionary/covariable/){.uri}.

We're going to perform [statistical tests](https://www.statisticssolutions.com/statistical-tests/) on the data and visualise the data.

## R programming

We're using R, which is free software that can be used on Mac's, Windows, or Linux-based computing systems.

You'll find that R is used extensively for data analysis, because it's very effective for statistical testing and for visualising data.

So you will come across it multiple times as a student, but also in general research.

Therefore, it's really important to understand how it works - but **you do not need to know every bit of code**, but rather what the code allows you to do and **how to interpret results**.

RStudio, is the user-interface for R which makes it easier for us to work with - rather than working on the command line!

So, just remember that the programming language is R, but the interface we usually work off of is RStudio.

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
