```{r title}
#| include: false
#| code-overflow: wrap

library("exams")
library("exams2forms")
ukdemo <- read.csv("~/../../Downloads/UKDemographic.csv")
ukdemo$Sex = as.factor(ukdemo$Sex)
ans1 = nrow(subset(ukdemo, Sex == "Female"))
ans2 = nrow(subset(ukdemo, Sex == "Male"))
```

Question
========
There are `r paste0('<span class="inline-solveme">', add_cloze(ans1), '</span>')` Females in the dataset, and `r paste0('<span class="inline-solveme">', add_cloze(ans2), '</span>')` Males in the dataset.

```{r boink}
#| echo: false
#| results: false
format_metainfo("answerlist")
```
Solution
========
You should be able to read the values from the summary() function.

If exact values are not returned, it's likely that you are either using the wrong column, or you did not import the data correctly. 

Look back at Step 1 to ensure that you have included Strings as factors, and re-read this section to understand why we do this.
Metainformation
===============
exname: female male diff
extype: cloze
exclozetype: `r format_metainfo("type")`
exsolution: `r format_metainfo("solution")`
extol: `r format_metainfo("tolerance")`
exshuffle: TRUE
