```{r sampling}
#| echo: false
#| results: hide
library(exams)
library(exams2forms)
MMILabData = read.csv("MMILabData.csv", header = T, stringsAsFactors = T, na.strings = " ")
MMILabData = MMILabData[-154,]
MMILabData = na.omit(MMILabData)
lm_results = summary(lm(MMILabData$Height ~ MMILabData$LengthLeftFoot))
lm_results2 = summary(lm(MMILabData$Height ~ MMILabData$Sex))
```

Question
========
1. **How much of the variation in Height can be predicted by LengthLeftFoot? ? Round to nearest whole number**

::: {style="padding-left: 2em;"}
`r add_cloze(round(lm_results[["adj.r.squared"]]*100))`
:::

2. **Perform another regression analysis for Height dependent on the LengthLeftFoot. Is LengthLeftFoot or Sex more powerful in predicting Height?**

::: {style="padding-left: 2em;"}
The LengthLeftFoot predicts ~ `r add_cloze(round(lm_results[["adj.r.squared"]]*100))` of the variation in height.

Sex predicts ~ `r add_cloze(round(lm_results2[["adj.r.squared"]]*100))` of the variation in height.

Therefore, Sex is slightly `r add_cloze("more", c("less","more"))` powerful than LengthLeftFoot in predicting Height.
:::

3. **Is this meaningfully better?**

::: {style="padding-left: 2em;"}
`r add_cloze("It's a small difference, so it's probably not meaningfully better.", c("It's a small difference, so it's probably not meaningfully better.", "Both are significant (p < 0.05), so therefore it is extremely meaningfully better."))`
:::

3. **What is the likely cause and effect relationship between LengthLeftFoot and Height?**

```{r table2}
#| echo: false
ans <- character(3)
sol <- logical(3)

ans[1] <- "Length of the left foot depends on height"
sol[1] <- FALSE

ans[2] <- "Height depends on the length of the left foot"
sol[2] <- FALSE

ans[3] <- "Both height and the length of the left foot are independent outcomes of sex"
sol[3] <- TRUE

ans[4] <- "There are likely other factors that affect height, like genetic variants, or maternal, foetal, and childhood nutrition"
sol[4] <- TRUE

```

::: {style="padding-left: 2em;"}
`r add_cloze(setNames(sol, ans), type = "mchoice")`
:::


`r format_metainfo("answerlist")`



Metainformation
===============
exname: penguins sex dimorphism
extype: cloze
exclozetype: `r format_metainfo("type")`
exsolution: `r format_metainfo("solution")`
extol: `r format_metainfo("tolerance")`
exshuffle: TRUE
